Re-Allocation of Resources during Releases \titlenote{Copyright note}

### 2013-12-05 paper1/paper1.tex
updating paper and added presentation slide, directory structure changed

\subsubsection{Explanation}
A Linux kernel development release version having maximum length of information does look like \textbf{linuxvA.B.C-rcP} where A, B, C, P are numeric. If a release version looks like ``linuxv2.6.13'' it tells us that this particular release is the 13th minor release in the series of the 6th major release of kernel version 2. ``linuxv2.6.13\textbf{-rc1}'' says that after the 12th stable minor release had published, development for the next release has been started and rc1 is the first candidate on the way to the next release. It also ensures that next release is going to be another minor release which is ``linuxv2.6.13''. We have last couple of release candidates for ``linuxv2.6.12'' and first couple of release candidates for ``linuxv3.12'' which is not useful for our calculation. So we are having 340 releases including major, minor, micro and rc; 39 stable releases from ``linuxv2.6.11'' to ``linuxv3.11'' having complete data with us. We have total 400441 distinct commits and for 372943 of them have change information for 77082 different files in our hand where we have 14599 developers' working history among 14621 distinct developers. Surprisingly 14569 individual files didn't have any change (addition or deletion) but was being committed at least once. So we found them in our released wise datasets.

@@

In order to see how many developers contribute to the new feature developments and how many contribute in merging and fixing, review and accepting codes from the community during the development period, we observed the developers' area in Development Period and developers' area in Release Period. Out of all 381152 commits belonging to all 331 releases 292926 commits were made during the time of development period which is 76.85\% (more than 2/3) of the total. These commits were made by 14621 individual developers. We now keeping only the records belong to release 2.6.13 to 3.11 because we have complete information for these releases, so we had to remove the commit records belong to linuxv2.6.12 and linuxv3.12 and later. 11209 developers work in development period and 7625 developers work around the release period.

@@

\begin{figure}
\begin{center}
\includegraphics[height=1.7in,width=3.4in]{devsMPRP.png}
\caption{\small \sl Increasing contribution in RDP}
\end{center}
\end{figure}

@@

We analyzed in several releases and found that for the release ``linuxv2.6.13'' 2938 files got churned. Among them only five files had exceptionally high number of churns four of them have more than 10,000 churns. Similar picture we see for other releases also. Usually around 2000 files are worked on during the release periods except 2 releases where the number of churned files was extremely high and being marked as outliers as shown in figure 12. For almost every release cycle during the release period around 2.846 files get highly increased attention having over 5000 churns and 16.78 files having over 1000 churns as shown in figure 13.
\begin{figure}
\begin{center}
\includegraphics[height=1.7in,width=3in]{fileChurnRPbox.png}
\caption{\small \sl Files churned in release periods}
\end{center}
\end{figure}

>>>>

\subsubsection{Explanation}
A Linux kernel development release version having maximum length of information does look like \textbf{linuxvA.B.C-rcP} where A, B, C, P are numeric. If a release version looks like ``linuxv2.6.13'' it tells us that this particular release is the 13th minor release in the series of the 6th major release of kernel version 2. ``linuxv2.6.13\textbf{-rc1}'' says that after the 12th stable minor release had published, development for the next release has been started and rc1 is the first candidate on the way to the next release. It also ensures that next release is going to be another minor release which is ``linuxv2.6.13''. We have last couple of release candidates for ``linuxv2.6.12'' and first couple of release candidates for ``linuxv3.12'' which is not useful for our calculation. So we are having 340 releases including major, minor, micro and rc; 39 stable releases from ``linuxv2.6.11'' to ``linuxv3.11'' having complete data with us. We have total 400441 distinct commits and for 372943 of them have change information for 77082 different files in our hand where we have 13926 developers' commit history among 14621 distinct developers. Surprisingly 14569 individual files didn't have any change (addition or deletion) but was being committed at least once. So we found them in our released wise datasets.

@@

In order to see how many developers contribute to the new feature developments and how many contribute in merging and fixing, review and accepting codes from the community during the development period, we observed the developers' area in Development Period and developers' area in Release Period. Out of all 381152 commits belonging to all 331 releases 292926 commits were made during the time of development period which is 76.85\% (more than 2/3) of the total. These commits were made by 13926 individual developers. We now keeping only the records belong to release 2.6.13 to 3.11 because we have complete information for these releases, so we had to remove the commit records belong to linuxv2.6.12 and linuxv3.12 and later. 11209 developers work in development period and 7625 developers work around the release period.

@@

\begin{figure}
\begin{center}
\includegraphics[height=1.7in,width=3.4in]{devsMPRP.png}
\caption{\small \sl Increasing contribution in DP}
\end{center}
\end{figure}

@@

We analyzed in several releases and found that for the release ``linuxv2.6.13'' 2938 files got churned. Among them only five files had exceptionally high number of churns four of them have more than 10,000 churns. Similar picture we see for other releases also. Usually around 2000 files are worked on during the release periods except 2 releases where the number of churned files was extremely high and being marked as outliers as shown in figure 12. For almost every release cycle during the release period around 2.846 files get highly increased attention having over 5000 churns and 16.78 files having over 1000 churns as shown in figure 13.
\begin{figure}
\begin{center}
\includegraphics[height=1.7in,width=3in]{fileChurnRPbox.png}
\caption{\small \sl Number of Files churned in release periods}
\end{center}
\end{figure}
